---
title: "Groundwater"
author: "Michael Rustler"
date: "`r Sys.time()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Groundwater}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
# Should the data of only a subset of stations be downloaded?
use_random_subset_of_stations <- FALSE

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Define URLs and Helper Functions

```{r}
`%>%` <- magrittr::`%>%`

urls <- kwb.utils::resolve(list(
  gh_wasserportal = "https://kwb-r.github.io/wasserportal",
  stations_gwl_meta = "<gh_wasserportal>/stations_gwl_master.json",
  stations_gwl_data = "<gh_wasserportal>/stations_gwl_data.json",
  stations_gwq_meta = "<gh_wasserportal>/stations_gwq_master.json",
  stations_gwq_data = "<gh_wasserportal>/stations_gwq_data.json",
  stations_crosstable = "<gh_wasserportal>/stations_crosstable.json"
))

top_filter_data_table <- function(data) {
  DT::datatable(data, filter = "top")
}

cat_file_enumeration <- function(base_url, files) {
  cat(paste0(
    sprintf("- [%s](%s/%s)", files, base_url, files),
    collapse = "\n\n"
  ))
}
```

## Master Data

```{r master_data}
stations <- wasserportal::get_stations()

is_gw <- stringr::str_detect(names(stations$overview_list), "groundwater")

files <- wasserportal::list_masters_data_to_csv(stations$overview_list[is_gw])
```

The following groundwater master data `.csv` files are available for download: 

```{r master_data_csv, echo = FALSE, results ='asis'}
cat_file_enumeration(urls$gh_wasserportal, files)
```

## Get Groundwater Data

```{r groundwater_data_raw_export}
if (use_random_subset_of_stations) {
  stations_bak <- stations
  x <- stations$overview_list$groundwater.level[sample(876, 10), ]
  stations$overview_list$groundwater.level <- x
  x <- stations$overview_list$groundwater.quality[sample(208, 10), ]
  stations$overview_list$groundwater.quality <- x
}

gw_data_list <- wasserportal::get_groundwater_data(stations, debug = TRUE)

files <- wasserportal::list_timeseries_data_to_zip(gw_data_list)

files

# Data availability per parameter
gw_data_list %>%
  dplyr::bind_rows() %>% 
  dplyr::count(Parameter, Einheit) %>% 
  dplyr::arrange(dplyr::desc(.data$n))
```

The following groundwater data `.zip` files are available for download: 

```{r groundwater_data_zip, echo = FALSE, results ='asis'}
cat_file_enumeration(urls$gh_wasserportal, files)
```

## Do Your Own Analysis! 

Download CSV/JSON/ZIP files scraped and prepared each day at 5 a.m. UTC for
re-use in R. The following data are available:

- **Data availability**

* [stations_crosstable.json](`r urls$stations_crosstable`): 
available parameters per station (see `wasserportal::get_overview_options()` 
for available options). Note: includes also surface monitoring stations!

```{r stations_crosstable}
library(wasserportal)

stations_crosstable <- jsonlite::fromJSON(urls$stations_crosstable)

str(stations_crosstable)
```

- **Master Data**

* [stations_gwl_master.json](`r urls$stations_gwl_meta`): 
for GW level stations

* [stations_gwq_master.json](`r urls$stations_gwq_meta`): 
for GW quality stations

- **Measurements**

* [stations_gwl_data.json](`r urls$stations_gwl_data`): 
GW level measurements for stations

* [stations_gwq_data.json](`r urls$stations_gwq_data`): 
GW quality measurements for all available parameters and stations

Please find an example below for merging all this information into a single 
data frame:

```{r }
library(wasserportal)

site_number_to_character <- function(data) {
  data %>%
    dplyr::mutate(
      Messstellennummer = as.character(.data$Messstellennummer)
    )
}

left_join_by_site <- function(data, master_data) {
  data %>%
    dplyr::left_join(master_data, by = c("Messstellennummer" = "Nummer"))
}

### GW levels
gwl_master <- jsonlite::fromJSON(urls$stations_gwl_meta)
gwl_data <- jsonlite::fromJSON(urls$stations_gwl_data) %>%  
  site_number_to_character() %>% 
  left_join_by_site(gwl_master)

str(gwl_data)

### GW quality (all available parameters!)
gwq_master <- jsonlite::fromJSON(urls$stations_gwq_meta)
gwq_data <- jsonlite::fromJSON(urls$stations_gwq_data) %>%  
  site_number_to_character() %>% 
  left_join_by_site(gwq_master)

str(gwq_data)

### Merge GW level and quality into one data frame
gw_data <- dplyr::bind_rows(gwl_data, gwq_data)

str(gw_data)
```

## Data Availability 

### GW Quality

```{r stations_gwq_data_helpers}
# Helper functions to be reused in different data summaries
select_main_columns <- function(data) {
  data %>%
    dplyr::select(dplyr::all_of(c(
      "Messstellennummer",
      "Parameter",
      "Datum",
      "Messwert"
    )))
}

summarise_min_max_n_arrange <- function(data) {
  data %>%
    dplyr::summarise(
      date_min = min(.data$Datum),
      date_max = max(.data$Datum),
      n = dplyr::n(), 
      .groups = "drop"
    ) %>%
    dplyr::arrange(dplyr::desc(.data$n))
}
```

```{r stations_gwq_data_by_parameter_table}
gwq_data_by_parameter <- gwq_data %>%
    select_main_columns() %>%
    dplyr::group_by(.data$Parameter) %>%
    summarise_min_max_n_arrange()

top_filter_data_table(gwq_data_by_parameter)
```

```{r stations_gwq_data_by_parameter_and_station_table}
gwq_data_by_parameter_and_station <- gwq_data %>%
  select_main_columns() %>%
  dplyr::group_by(.data$Parameter, .data$Messstellennummer) %>%
  summarise_min_max_n_arrange()

top_filter_data_table(gwq_data_by_parameter_and_station)
```

## Export

### GW Quality

```{r export_xlsx_gwq, eval = FALSE}
openxlsx::write.xlsx(
  x = list(
  gwq_by_parameter = gwq_data_by_parameter,
  gwq_by_parameter_and_station = gwq_data_by_parameter_and_station,
  gwq_data = gwq_data,
  gwq_master = gwq_master
),
  file = "wasserportal_gwq_data.xlsx",
  overwrite = TRUE
)
```
