---
title: "Groundwater"
author: "Michael Rustler"
date: "`r Sys.time()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Groundwater}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Do Your Own Analysis! 

Download JSON files scraped and prepared each day at 5 a.m. UTC for re-use in R. 
The following data are available:

- **Data availability**

   * [stations_crosstable.json](https://kwb-r.github.io/wasserportal/stations_crosstable.json): 
   available parameters per station (see `wasserportal::get_overview_options()` 
   for available options). Note: includes also surface monitoring stations!
   

```{r stations_crosstable}
library(wasserportal)

stations_crosstable <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_crosstable.json")

str(stations_crosstable)
       
```

- **Master Data**

   * [stations_gwl_master.json](https://kwb-r.github.io/wasserportal/stations_gwl_master.json): 
     for GW level stations

   * [stations_gwq_master.json](https://kwb-r.github.io/wasserportal/stations_gwq_master.json): 
     for GW quality stations
     
- **Measurements**

   * [stations_gwl_data.json](https://kwb-r.github.io/wasserportal/stations_gwl_master.json): 
     GW level measurements for stations

   * [stations_gwq_master.json](https://kwb-r.github.io/wasserportal/stations_gwq_master.json): 
     GW quality measurements for all available parameters and stations

Please find an example below for merging all this information into a single 
data frame:

```{r }
library(wasserportal)

### GW levels
gwl_master <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwl_master.json")
gwl_data <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwl_data.json") %>%  
  dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
  dplyr::left_join(gwl_master, by = c("Messstellennummer" = "Nummer"))

str(gwl_data)

### GW quality (all available parameters!)
gwq_master <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwq_master.json")
gwq_data <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwq_data.json") %>%  
  dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
  dplyr::left_join(gwq_master, by = c("Messstellennummer" = "Nummer"))

str(gwq_data)

### Merge GW level and quality into one data frame
gw_data <- dplyr::bind_rows(gwl_data, gwq_data)

str(gw_data)

```

## Data Availability 

### GW Quality

```{r stations_gwq_data_by_parameter_table}
gwq_data_by_parameter <- gwq_data %>%
  dplyr::select(.data$Messstellennummer,
                .data$Parameter,
                .data$Datum,
                .data$Messwert) %>%
  dplyr::group_by(.data$Parameter) %>%
  dplyr::summarise(date_min = min(.data$Datum),
                   date_max = max(.data$Datum),
                   n = dplyr::n()) %>%
  dplyr::arrange(dplyr::desc(.data$n))

DT::datatable(gwq_data_by_parameter, filter = "top")
```

```{r stations_gwq_data_by_parameter_and_station_table}
gwq_data_by_parameter_and_station <-  gwq_data %>%
  dplyr::select(.data$Messstellennummer,
                .data$Parameter,
                .data$Datum,
                .data$Messwert) %>%
  dplyr::group_by(.data$Parameter,
                  .data$Messstellennummer) %>%
  dplyr::summarise(date_min = min(.data$Datum),
                   date_max = max(.data$Datum),
                   n = dplyr::n()) %>%
  dplyr::arrange(dplyr::desc(.data$n))

DT::datatable(gwq_data_by_parameter_and_station, filter = "top")
```

## Export

### GW Quality

```{r export_xlsx_gwq, eval = FALSE}
gwq_data_list <- list(gwq_by_parameter = gwq_data_by_parameter,
                              gwq_by_parameter_and_station = gwq_data_by_parameter_and_station,
                              gwq_data = gwq_data,
                              gwq_master = gwq_master)

openxlsx::write.xlsx(x = gwq_data_list,
                     file = "wasserportal_gwq_data.xlsx",
                     overwrite = TRUE)
```
