---
title: "Groundwater"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Groundwater}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Do Your Own Analysis! 

Download JSON files scraped and prepared each day at 5 am UTc for re-use in R. 
The following data are available:

- **Master Data**
   * [stations_gwl_master.json](https://kwb-r.github.io/wasserportal/stations_gwl_master.json): 
     for GW level stations
   * [stations_gwq_master.json](https://kwb-r.github.io/wasserportal/stations_gwq_master.json): 
     for GW quality stations
     
- **Measurements**
   * [stations_gwl_data.json](https://kwb-r.github.io/wasserportal/stations_gwl_master.json): 
     GW level measurements
   * [stations_gwq_master.json](https://kwb-r.github.io/wasserportal/stations_gwq_master.json): 
     for GW quality stations

Please find an example below for merging all this information into a single 
data frame:

```{r }
library(wasserportal)

### GW levels
gwl_master <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwl_master.json")
gwl_data <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwl_data.json") %>%  
  dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
  dplyr::left_join(gwl_master, by = c("Messstellennummer" = "Nummer"))

str(gwl_data)

### GW quality (all available parameters!)
gwq_master <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwq_master.json")
gwq_data <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwq_data.json") %>%  
  dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
  dplyr::left_join(gwq_master, by = c("Messstellennummer" = "Nummer"))

str(gwl_data)

### Merge GW level and quality into one data frame
gw_data <- dplyr::bind_rows(gwl_data, gwq_data)

str(gw_data)

```
