---
title: "PROMISCES: Norman Lists"
author: "Michael Rustler"
date: "`r Sys.time()`"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{PROMISCES: Norman Lists}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
is_ghactions <- identical(Sys.getenv("CI"), "true")
```

## Install R Package

```{r eval=FALSE}
# Enable this universe
options(repos = c(
  kwbr = 'https://kwb-r.r-universe.dev',
  CRAN = 'https://cloud.r-project.org'))

# Install R package
install.packages('wasserportal')

```

## Get Norman Lists

```{r eval = is_ghactions}
library(wasserportal)

download_file <- function(url, 
                            tdir = tempdir()
) {
filename <- basename(url)
t_path <- file.path(tdir, filename)
download.file(url, dest= t_path, mode="wb") 
t_path
}

### Download S0 | SUSDAT | Merged NORMAN Suspect List: SusDat
### Version: NORMAN-SLE-S0.0.4.1 (2021-01-18)
### DOI: 10.5281/zenodo.5873975

norman_s0_path  <- download_file("https://zenodo.org/record/5873975/files/susdat_2022-01-18-104316.csv")
norman_s0 <- readr::read_csv(norman_s0_path)

### Download S36 | UBAPMT | Potential Persistent, Mobile and Toxic (PMT) substances
### Version: NORMAN-SLE-S36.0.2.1 (2020-12-15)
### DOI: "10.5281/zenodo.4323239"

norman_s36_ubapmt_path  <- download_file("https://zenodo.org/record/4323239/files/S36_UBAPMT_Dec2020.csv")
norman_s36_ubapmt <- readr::read_csv(norman_s36_ubapmt_path)


### Download S90 | ZEROPMBOX1 | ZeroPM Box 1 Substances
### Version: Version NORMAN-SLE-S90.0.1.0 (2021-01-15)
### DOI: 10.5281/zenodo.5854252

norman_s90_zeropm_path  <- download_file("https://zenodo.org/record/5854252/files/ZeroPM_Box1.csv")
norman_s90_zeropm <- readr::read_csv(norman_s90_zeropm_path)


cas_wasserportal <- wasserportal::readPackageFile(file = "cas_wasserportal.csv",
                                                  encoding = "UTF-8")
cas_reach <- wasserportal::readPackageFile(file = "cas_reach.csv")

ubapmt_publication <- cas_reach %>%
  dplyr::filter(.data$cas_number %in% unique(cas_wasserportal$cas_number))


ubapmt_zenodo <- norman_s36_ubapmt %>%
  dplyr::filter(.data$CAS_Number %in% unique(cas_wasserportal$cas_number)) %>%
  dplyr::rename(cas_number = .data$CAS_Number)

missing_on_zenodo <- cas_reach %>%
  dplyr::mutate(zenodo = dplyr::if_else(.data$cas_number %in% unique(ubapmt_zenodo$cas_number),
                                        "yes",
                                        NA_character_),
                publication = dplyr::if_else(.data$cas_number %in% unique(ubapmt_publication$cas_number),
                                        "yes",
                                        NA_character_)) %>%
  dplyr::filter(publication == "yes" | zenodo == "yes") %>%
  dplyr::relocate(tidyselect::all_of(c("publication", "zenodo")), .before = .data$emission_likelihood)


DT::datatable(missing_on_zenodo, filter = "top", rownames = FALSE)


norman_s0_in_wasserportal <- norman_s0 %>%
  dplyr::mutate(cas_number = stringr::str_remove(.data$CAS_RN_Dashboard,
                                                 pattern = "^CAS_RN:\\s")) %>%
  dplyr::filter(!is.na(.data$cas_number),
                .data$cas_number %in% unique(cas_wasserportal$cas_number))


#DT::datatable(norman_s0_in_wasserportal, filter = "top", rownames = FALSE)

norman_lists_table <- xml2::read_html("https://www.norman-network.com/nds/SLE/") %>%
rvest::html_element(css = ".table") %>%
rvest::html_table() %>%
janitor::clean_names()

DT::datatable(norman_lists_table)

```

                  

## Get GW Quality from Wasserportal

```{r eval = is_ghactions}
# Load R package

### For details see:
### https://kwb-r.github.io/wasserportal/articles/groundwater.html
### JSON files (see below) are build every day automatically at 5a.m. with
### continious integration, for build status, see here:
### https://github.com/KWB-R/wasserportal/actions/workflows/pkgdown.yaml

### GW quality (all available parameters!)
gwq_master <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwq_master.json")
gwq_data <- jsonlite::fromJSON("https://kwb-r.github.io/wasserportal/stations_gwq_data.json") %>%
  dplyr::filter(.data$Parameter %in% cas_wasserportal$Parameter) %>%
  dplyr::inner_join(cas_wasserportal, by = "Parameter") %>%
  dplyr::inner_join(norman_s0_in_wasserportal, by = "cas_number") %>% 
  dplyr::filter(.data$logKow_EPISuite <= 4.5,
                !is.na(.data$`LC50_48_hr_ug/L`)) %>% 
  dplyr::mutate(Messstellennummer = as.character(Messstellennummer),
## CensorCode: either "below" (less than) for concentration below detection limit
## (value is detection limit) or "nc" (not censored) for concentration above
## detection limit
                CensorCode = dplyr::case_when(Messwert <= 0 ~ "lt",
                                              TRUE ~ "nc"),
                Messwert = dplyr::case_when(Messwert < 0 ~ abs(Messwert),
### Only two decimal numbers are exported by Wasserportal, but some sustances
### have lower detection limit, e.g. 0.002 which results in -0.00 export, thus
### the dummy detection limit 0.00999 was introduced (until fixed by Senate:
### Christoph will sent a email to Matthias Schröder)
                                            Messwert == 0 ~ 0.009999,
                                            TRUE ~ Messwert)) %>%
  dplyr::left_join(gwq_master, by = c("Messstellennummer" = "Nummer"))

gwq_subs <- gwq_data %>%
  dplyr::count(.data$cas_number, .data$CensorCode) %>%
  tidyr::pivot_wider(names_from = CensorCode, values_from = n) %>%
  dplyr::mutate(lt = ifelse(is.na(lt), 0, lt),
                nc = ifelse(is.na(nc), 0, nc),
                n_total = lt + nc,
                percent_nc = 100*nc/n_total) %>%
  dplyr::rename(n_lt = lt,
                n_nc = nc) %>%
  dplyr::left_join(norman_s0_in_wasserportal) %>%
  dplyr::rename(name_norman = .data$Name_Dashboard)

 readr::write_csv(gwq_subs, "gwq_subs.csv")
 DT::datatable(gwq_subs, filter = "top", rownames = FALSE)

samples <- gwq_data %>%
   dplyr::rename(name_norman = .data$Name_Dashboard) %>%
   dplyr::select(name_norman,
                 cas_number,
                 Messstellennummer,
                 Datum,
                 CensorCode,
                 Messwert,
                 Einheit)


samples_by_para_and_station <- gwq_data %>%
  dplyr::count(.data$cas_number,
                  .data$Messstellennummer,
                  .data$CensorCode) %>%
  tidyr::pivot_wider(names_from = CensorCode, values_from = n) %>%
  dplyr::mutate(lt = ifelse(is.na(lt), 0, lt),
                nc = ifelse(is.na(nc), 0, nc),
                n_total = lt + nc,
                percent_nc = 100*nc/n_total) %>%
  dplyr::rename(n_lt = lt,
                n_nc = nc) %>%
  dplyr::left_join(norman_s0_in_wasserportal) %>%
  dplyr::rename(name_norman = .data$Name_Dashboard) %>%
  dplyr::left_join(gwq_master, by = c(Messstellennummer = "Nummer")) %>%
  dplyr::arrange(dplyr::desc(percent_nc))


# samples_by_category_and_station <- samples_by_para_and_station  %>%
#   dplyr::group_by(.data$category,
#                   .data$category_name,
#                   .data$Messstellennummer) %>%
#   dplyr::summarise(n_lt = sum(n_lt),
#                    n_nc = sum(n_nc),
#                    n_total = sum(n_total)) %>%
#   dplyr::mutate(percent_nc = 100*n_nc/n_total) %>%
#   dplyr::arrange(dplyr::desc(percent_nc))

gwq_subs_stations_n_abovedetection <- samples_by_para_and_station  %>%
  dplyr::filter(n_nc > 0) %>%
  dplyr::group_by(.data$cas_number) %>%
  dplyr::summarise(n_stations_abovedetection = dplyr::n())

gwq_subs_stations_n_paras_abovedetection <- samples_by_para_and_station  %>%
  dplyr::filter(n_nc > 0) %>%
  dplyr::group_by(#.data$category,
                  #.data$category_name,
                  .data$Messstellennummer) %>%
  dplyr::summarise(n_paras_abovedetection = dplyr::n()) %>%
  dplyr::left_join(gwq_master, by = c("Messstellennummer" = "Nummer"))

# gwq_subs_stations_n_paras_abovedetection_wide <- gwq_subs_stations_n_paras_abovedetection %>%
#   dplyr::ungroup() %>%
#   dplyr::select(Messstellennummer, category, n_paras_abovedetection) %>%
#   tidyr::pivot_wider(names_from = "category",
#                      names_prefix = "cat_",
#                      values_from = "n_paras_abovedetection") %>%
#   dplyr::left_join(gwq_master, by = c("Messstellennummer" = "Nummer"))


samples_by_para_and_station_n <- samples_by_para_and_station %>%
  dplyr::group_by(name_norman,
                  cas_number) %>%
  dplyr::summarise(n_stations_sampled = dplyr::n(),
                   n_stations_total = length(unique(gwq_master$Nummer)),
                   n_lt = sum(n_lt),
                   n_nc = sum(n_nc),
                   n_total = sum(n_total)) %>%
  dplyr::left_join(gwq_subs_stations_n_abovedetection) %>%
  dplyr::mutate(n_stations_abovedetection = ifelse(is.na(n_stations_abovedetection),
                                                   0,
                                                   n_stations_abovedetection),
                n_abovedetection = ifelse(is.na(n_nc), 0, n_nc),
                n_belowdetection = ifelse(is.na(n_lt), 0, n_lt),
                percent_samples_abovedetection = 100*n_nc/n_total,
                percent_stations_abovedetection = 100*n_stations_abovedetection/n_stations_total,
                percent_stations_sampled = 100*n_stations_sampled/n_stations_total) %>%
  dplyr::select(name_norman,
                cas_number,
                n_stations_abovedetection,
                n_stations_sampled,
                n_stations_total,
                percent_stations_abovedetection,
                percent_stations_sampled,
                n_belowdetection,
                n_abovedetection,
                n_total,
                percent_samples_abovedetection) %>%
  dplyr::arrange(dplyr::desc(percent_stations_abovedetection),
                 dplyr::desc(percent_samples_abovedetection))





### Export data to EXCEL
gwq_data_list <- list(norman_lists_table = norman_lists_table, 
                      cas_wasserportal = cas_wasserportal,
                      cas_reach = cas_reach, 
                      ubapmt_missing_on_zenodo = missing_on_zenodo,
                      norman_s0_in_wasserportal = norman_s0_in_wasserportal,
                      samples = samples,
                      samples_by_para = gwq_subs %>%
                        dplyr::arrange(dplyr::desc(percent_nc)),
                      samples_by_para_and_station = samples_by_para_and_station,
                      samples_by_para_and_station_n = samples_by_para_and_station_n)
                      #samples_by_stations_para_above = gwq_subs_stations_n_paras_abovedetection_wide)
                      #samples_by_category_and_station = samples_by_category_and_station)



openxlsx::write.xlsx(x = gwq_data_list,
                     file = "wasserportal_gwq_norman-list_s0_v1.0.0.xlsx",
                     overwrite = TRUE)
```

## Norman Substances in Wasserportal 

Filter criteria:
  - log Kow (column `logKow_EPISuite` <= `4.5`)
  - toxicity value (column `LC50_48_hr_ug/` not `NA`)

```{r eval = is_ghactions, fig.height = 14, fig.width = 7}


gwq_subs_plot <- samples_by_para_and_station_n %>% 
  dplyr::filter(.data$percent_samples_abovedetection > 0) %>% 
  dplyr::left_join(norman_s0_in_wasserportal) %>%
  dplyr::arrange(.data$`LC50_48_hr_ug/L`) %>% 
  dplyr::mutate(label = sprintf("%s (%s, LC50_48_hr_ug/L: %.1f, logKow_EPISuite: %.1f : ", 
                                .data$name_norman, 
                                .data$cas_number,
                                .data$`LC50_48_hr_ug/L`,
                                .data$logKow_EPISuite
                                ))

gwq_subs_plot$label <- as.factor(gwq_subs_plot$label)
g1 <- gwq_subs_plot %>% 
  ggplot2::ggplot(ggplot2::aes(x = .data$percent_samples_abovedetection, 
                               y = forcats::fct_reorder(.data$label, .data$percent_samples_abovedetection, .desc = TRUE),
                               label = sprintf("%2.2f %% (n_samples = %d, n_stations = %d)", .data$percent_samples_abovedetection,.data$n_total, .data$n_stations_sampled),
                               fill = .data$logKow_EPISuite)) +                             
  #ggplot2::scale_fill_brewer(palette="RdYlGn") +      
  ggplot2::scale_y_discrete(limits = rev) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::geom_text(size = 1.8, hjust = -0.01) +
  ggplot2::xlim(c(0,120)) +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "top") +
  ggplot2::labs(#subtitle = sprintf("%d / %d substances (>= 1 value above detection limit)",
                #                sum(gwq_subs_plot$n_abovedetection > 0),
                #                   nrow(gwq_subs_plot)),                         
                y = "", 
                x = "Percent of Samples above Detection Limit (%)")

g1

ggplot2::ggsave(filename = "wasserportal_norman-s0-substances_only-above-detection-limit.jpeg", 
                  plot = g1,
                  width = 40, 
                  height = 20,
                  units = "cm")
``` 

<!-- ```{r} -->


<!-- wasserportal_substances_plot <- wasserportal_substances %>% -->
<!--   dplyr::mutate(label = sprintf("%s (%s, stations: %d)",  -->
<!--                                 .data$name_uba,  -->
<!--                                 .data$cas_number,  -->
<!--                                 .data$n_stations_sampled), -->
<!--                 category = forcats::as_factor(.data$category)) -->

<!-- wasserportal_substances_plot$label <- factor(wasserportal_substances_plot$label,  -->
<!--                                              levels = wasserportal_substances_plot$label) -->
<!-- wasserportal_substances_plot %>%  -->
<!--   ggplot2::ggplot(ggplot2::aes(x = .data$n_total,  -->
<!--                                y = .data$label,  -->
<!--                                label = .data$n_total, -->
<!--                                fill = .data$category)) + -->
<!--   ggplot2::scale_y_discrete(limits = rev) + -->
<!--   ggplot2::geom_bar(stat = "identity") + -->
<!--   ggplot2::geom_text(size = 2, nudge_x = -1) + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::labs(subtitle = sprintf("%d Wasserportal substances (listed in UBA table)", -->
<!--                                 nrow(wasserportal_substances_plot)), -->
<!--                 y = "",  -->
<!--                 x = "Number of Samples") -->


<!-- ``` -->


<!-- ```{r} -->

<!-- gwq_subs_plot <- samples_by_para_and_station_n %>%  -->
<!--   dplyr::mutate(label = sprintf("Cat %d: %s (%s)",  -->
<!--                                 .data$category, -->
<!--                                 .data$name_uba,  -->
<!--                                 .data$cas_number), -->
<!--                 category = forcats::as_factor(.data$category)) -->

<!-- gwq_subs_plot$label <- as.factor(gwq_subs_plot$label) -->
<!-- g1 <- gwq_subs_plot %>%  -->
<!--   ggplot2::ggplot(ggplot2::aes(x = .data$percent_samples_abovedetection,  -->
<!--                                y = forcats::fct_reorder(.data$label, .data$percent_samples_abovedetection, .desc = TRUE), -->
<!--                                label = sprintf("%2.2f %% (n_samples = %d, n_stations = %d)", .data$percent_samples_abovedetection,.data$n_total, .data$n_stations_sampled), -->
<!--                                fill = .data$category)) +                             ggplot2::scale_fill_brewer(palette="RdYlGn") +       -->
<!--   ggplot2::scale_y_discrete(limits = rev) + -->
<!--   ggplot2::geom_bar(stat = "identity") + -->
<!--   ggplot2::geom_text(size = 1.8, hjust = -0.01) + -->
<!--   ggplot2::xlim(c(0,40)) + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::theme(legend.position = "top") + -->
<!--   ggplot2::labs(subtitle = sprintf("%d / %d substances (>= 1 value above detection limit)", -->
<!--                                 sum(gwq_subs_plot$n_abovedetection > 0), -->
<!--                                    nrow(gwq_subs_plot)),                          -->
<!--                 y = "",  -->
<!--                 x = "Percent of Samples above Detection Limit (%)") -->

<!-- g1 -->

<!-- ggplot2::ggsave(filename = "wasserportal_reach-substances_above-detection-limit.jpeg",  -->
<!--                   plot = g1, -->
<!--                   width = 17,  -->
<!--                   height = 17, -->
<!--                   units = "cm") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- n_cat <- samples_by_category_and_station %>%  -->
<!--   dplyr::group_by(Messstellennummer) %>%   -->
<!--   dplyr::summarise(n_samples_abovedetection = sum(n_nc), -->
<!--                    n_samples_total = sum(n_total), -->
<!--                    n_samples_percent_abovedetection = 100*sum(n_nc)/sum(n_total)) %>%  -->
<!--   dplyr::arrange(dplyr::desc(.data$n_samples_abovedetection)) -->

<!-- g1 <- samples_by_category_and_station %>%  -->
<!--   dplyr::left_join(n_cat) %>%  -->
<!--   dplyr::filter(n_nc > 0)  %>%  -->
<!--   dplyr::mutate(Messstellennummer = as.factor(Messstellennummer), -->
<!--                 category = as.factor(category)) %>%   ggplot2::ggplot(ggplot2::aes(x = .data$n_nc,  -->
<!--                              y = forcats::fct_reorder(.data$Messstellennummer, .data$n_samples_abovedetection, .desc = TRUE), -->
<!--                                label = .data$n_nc, -->
<!--                                fill = .data$category)) +    -->
<!--   ggplot2::scale_fill_brewer(palette="RdYlGn") +       -->
<!--   ggplot2::scale_y_discrete(limits = rev) + -->
<!--   ggplot2::geom_col() + -->
<!--   ggplot2::geom_text(size = 1.8,  -->
<!--                      position = ggplot2::position_stack(vjust = 0.5 )) + -->
<!--   ggplot2::geom_text(mapping = ggplot2::aes( -->
<!--     x = .data$n_samples_abovedetection, -->
<!--     y = forcats::fct_reorder(.data$Messstellennummer, .data$n_samples_abovedetection, .desc = TRUE), -->
<!--     label = sprintf("%3.1f %% (n_samples = %d)", .data$n_samples_percent_abovedetection, .data$n_samples_total)), -->
<!--                      inherit.aes = FALSE, -->
<!--                      size = 1.8,  -->
<!--                      position = ggplot2::position_nudge(x = 20), -->
<!--     fontface = "bold") + -->
<!--   ggplot2::xlim(c(0,215)) + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::theme(legend.position = "top") + -->
<!--   ggplot2::labs(subtitle = "",                         -->
<!--                 fill = "Category", -->
<!--                 y = "Monitoring Station",  -->
<!--                 x = "Number of Samples Above Detection Limit") -->

<!-- g1 -->

<!-- ggplot2::ggsave(filename = "wasserportal_reach-categories_above-detection-limit.jpeg",  -->
<!--                   plot = g1, -->
<!--                   width = 17,  -->
<!--                   height = 40, -->
<!--                   units = "cm") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- n_cat <- gwq_subs_stations_n_paras_abovedetection %>%  -->
<!--   dplyr::group_by(Messstellennummer) %>%   -->
<!--   dplyr::summarise(n_paras_abovedetection_total = sum(n_paras_abovedetection)) %>%  -->
<!--   dplyr::arrange(dplyr::desc(.data$n_paras_abovedetection_total)) -->

<!-- g1 <- gwq_subs_stations_n_paras_abovedetection %>%  -->
<!--   dplyr::left_join(n_cat) %>%  -->
<!--   dplyr::mutate(Messstellennummer = as.factor(Messstellennummer), -->
<!--                 category = as.factor(category)) %>%   ggplot2::ggplot(ggplot2::aes(x = .data$n_paras_abovedetection,  -->
<!--                              y = forcats::fct_reorder(.data$Messstellennummer, .data$n_paras_abovedetection_total, .desc = TRUE), -->
<!--                              label = .data$n_paras_abovedetection, -->
<!--                              fill = .data$category)) +    -->
<!--   ggplot2::scale_fill_brewer(palette="RdYlGn") +       -->
<!--   ggplot2::scale_y_discrete(limits = rev) + -->
<!--   ggplot2::geom_col() + -->
<!--   ggplot2::geom_text(size = 1.8,  -->
<!--                      position = ggplot2::position_stack(vjust = 0.5 )) + -->

<!--   #ggplot2::xlim(c(0,215)) + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::theme(legend.position = "top") + -->
<!--   ggplot2::labs(subtitle = "",                         -->
<!--                 fill = "Category", -->
<!--                 y = "Monitoring Station",  -->
<!--                 x = "Number of Parameters Above Detection Limit") -->

<!-- g1 -->

<!-- ggplot2::ggsave(filename = "wasserportal_reach-categories_paras-by-station_above-detection-limit.jpeg",  -->
<!--                   plot = g1, -->
<!--                   width = 17,  -->
<!--                   height = 40, -->
<!--                   units = "cm") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- gwq_subs_plot <- samples_by_para_and_station_n %>%  -->
<!--   dplyr::mutate(n_stations_belowdetection = .data$n_stations_sampled - .data$n_stations_abovedetection,  -->
<!--                 n_stations_notsampled = .data$n_stations_total - .data$n_stations_sampled) %>%  -->
<!--   dplyr::select("category", -->
<!--                 "category_name", -->
<!--                 "name_uba", -->
<!--                 "cas_number", -->
<!--                 "n_stations_abovedetection",  -->
<!--                 "n_stations_belowdetection", -->
<!--                 "n_stations_notsampled") %>%  -->
<!--   tidyr::pivot_longer(cols = tidyselect::starts_with("n_stations"), -->
<!--                       names_to = "station_type", -->
<!--                       values_to = "station_value") %>%  -->
<!--   dplyr::filter(.data$station_value > 0) %>%  -->
<!--   dplyr::mutate(station_type = stringr::str_remove(.data$station_type,  -->
<!--                                                    "n_stations_")) %>% -->
<!--   dplyr::mutate(station_type = kwb.utils::multiSubstitute(.data$station_type, -->
<!--                                                           list("abovedetection" = "above detection", -->
<!--                                                                "belowdetection" = "below detection",  -->
<!--                                                                "notsampled" = "not sampled"))) %>%  -->
<!--   dplyr::mutate(label = sprintf("Cat %d: %s (%s)",  -->
<!--                                 .data$category, -->
<!--                                 .data$name_uba,  -->
<!--                                 .data$cas_number), -->
<!--                 category = forcats::as_factor(.data$category)) -->

<!-- gwq_subs_plot$label <- as.factor(gwq_subs_plot$label) -->
<!-- g1 <- gwq_subs_plot %>%  -->
<!--   ggplot2::ggplot(ggplot2::aes(x = .data$station_value,  -->
<!--                                y = .data$label, -->
<!--                                label = .data$station_value, -->
<!--                                fill = forcats::fct_rev(.data$station_type))) + -->
<!--   ggplot2::scale_fill_manual(values = c("lightgrey", "darkgreen", "red")) +  -->
<!--   ggplot2::scale_y_discrete(limits = rev) + -->
<!--   ggplot2::geom_col(alpha = 0.75) + -->
<!--   ggplot2::geom_text(size = 1.8,  -->
<!--                      position = ggplot2::position_stack(vjust = 0.5 )) + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::theme(legend.position = "top") + -->
<!--   ggplot2::labs(title = "Groundwater Quality by Station",  -->
<!--                 fill = "",  -->
<!--                 caption = "above detection: number of stations with at least 1 sample above detection limit\nbelow detection: number of station with all samples below detection limit\nnot sampled: number of stations not sampled", -->
<!--                 subtitle = sprintf("for %d GW quality stations", -->
<!--                                    length(unique(gwq_master$Nummer))), -->
<!--                 y = "",  -->
<!--                 x = "Number of Monitoring Stations") -->

<!-- g1 -->

<!-- ggplot2::ggsave(filename = "wasserportal_reach-substances_by-monitoring-station.jpeg",  -->
<!--                   plot = g1, -->
<!--                   width = 17,  -->
<!--                   height = 17, -->
<!--                   units = "cm") -->

<!-- ``` -->

<!-- ```{r} -->

<!-- stations_abovedetection <- samples_by_para_and_station %>%  -->
<!--   dplyr::filter(.data$n_nc > 0) %>%  -->
<!--   dplyr::select(cas_number, Messstellennummer, n_nc, n_lt) %>%  -->
<!--   dplyr::arrange(.data$n_nc) -->

<!-- g1_data <- gwq_data %>%  -->
<!--   dplyr::right_join(y = stations_abovedetection,  -->
<!--                     by = c("cas_number", "Messstellennummer")) %>%  -->
<!--   dplyr::mutate(Datum = as.Date(Datum),  -->
<!--                 CensorCode = kwb.utils::multiSubstitute(.data$CensorCode, -->
<!--                                                           list("nc" = "above detection",  -->
<!--                                                                "lt" = "below detection")),  -->
<!--                 label = sprintf("%s (%s): %s (n_above = %d, n_below = %d)",  -->
<!--                                 .data$name,  -->
<!--                                 .data$cas_number, -->
<!--                                 .data$Messstellennummer, -->
<!--                                 .data$n_nc, -->
<!--                                 .data$n_lt))  -->

<!-- labels <- unique(g1_data$label) -->

<!-- plot_timeseries <- function(sel_label) { -->
<!--   g1_data %>%  -->
<!--   dplyr::filter(.data$label == sel_label) %>%  -->
<!--   dplyr::arrange(.data$n_nc, .data$label, .data$Datum) %>%  -->
<!--   ggplot2::ggplot(mapping = ggplot2::aes(x = .data$Datum,  -->
<!--                                          y = .data$Messwert, -->
<!--                                          col = .data$CensorCode -->
<!--                                          )) + -->
<!--   ggplot2::scale_color_manual(values = c("red", "darkgreen")) + -->
<!--   ggplot2::geom_point() + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::labs(title = sel_label) -->
<!-- } -->

<!-- g_plots <- lapply(labels, function(sel_label) {plot_timeseries(sel_label)}) -->

<!-- pdff <- "wasserportal_reach-substances_timeseries.pdf" -->
<!-- mp <- gridExtra::marrangeGrob(g_plots, nrow=1, ncol=1) -->
<!-- ggplot2::ggsave(pdff, -->
<!--                 plot = mp,  -->
<!--                 width = 30, -->
<!--                 height = 20,  -->
<!--                 units = "cm") -->


<!-- ``` -->

<!-- ```{r} -->

<!-- n_samples_all <- samples %>%  -->
<!--   dplyr::count(.data$name_uba) %>%  -->
<!--   dplyr::rename(n_all = "n") -->


<!-- n_samples_above <- samples %>%  -->
<!--   dplyr::filter(CensorCode == "nc") %>%  -->
<!--   dplyr::count(.data$name_uba) %>%  -->
<!--   dplyr::rename(n_above = "n") -->

<!-- n_samples <- dplyr::left_join(n_samples_all, n_samples_above) %>%  -->
<!--   dplyr::mutate(label = as.factor(sprintf("%s (n_above = %d, n_samples = %d)",  -->
<!--                                 .data$name_uba, -->
<!--                                 .data$n_above, -->
<!--                                 .data$n_all)) -->
<!--   ) -->

<!-- substances_above <- samples %>%  -->
<!-- dplyr::filter(CensorCode == "nc") %>%  -->
<!-- dplyr::pull(.data$name_uba) %>%  -->
<!-- unique() -->

<!-- detection_limits <- samples %>% -->
<!--   dplyr::filter(CensorCode == "lt", -->
<!--                 name_uba %in% substances_above) %>%  -->
<!--   dplyr::mutate(Messwert = dplyr::if_else(.data$Einheit == "mg/l", -->
<!--                                           true = .data$Messwert * 1000, -->
<!--                                           false = .data$Messwert), -->
<!--                 Einheit = dplyr::if_else(.data$Einheit == "mg/l", -->
<!--                                           true = "\u00B5g/l", -->
<!--                                           false = .data$Einheit), -->
<!--                 year = as.integer(format(as.Date(.data$Datum), format = "%Y"))) %>%  -->
<!--   dplyr::count(.data$name_uba, .data$year, .data$Messwert) %>%  -->
<!--   dplyr::left_join(n_samples)  -->


<!-- plot_detection_limits <- function(sel_sub) {   -->
<!-- g1 <- detection_limits %>%  -->
<!--   dplyr::filter(name_uba == sel_sub) %>%  -->
<!--   ggplot2::ggplot(mapping = ggplot2::aes(x = .data$year, -->
<!--                                          y = .data$n, -->
<!--                                          col = forcats::fct_rev(as.factor(.data$Messwert)))) + -->
<!--   ggplot2::scale_color_brewer(palette="RdYlGn") + -->
<!--   ggplot2::geom_point() +  -->
<!--   ggplot2::labs(title = sprintf("%s", sel_sub), -->
<!--                 x = "Year",  -->
<!--                 y = "Number of Samples below Detection Limit", -->
<!--                 col = "Detection Limit (\u00B5g/l)") + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::theme(legend.position = "top") -->
<!-- g1 -->
<!-- } -->

<!-- g_plots <- lapply(substances_above, function(sel_sub) {plot_detection_limits(sel_sub)}) -->

<!-- pdff <- "wasserportal_reach-substances_detection-limits.pdf" -->
<!-- mp <- gridExtra::marrangeGrob(g_plots, nrow=1, ncol=1) -->
<!-- ggplot2::ggsave(pdff, -->
<!--                 plot = mp,  -->
<!--                 width = 20, -->
<!--                 height = 15,  -->
<!--                 units = "cm") -->


<!-- g1 <- samples %>% -->
<!--   dplyr::left_join(n_samples) %>%  -->
<!--   dplyr::filter(CensorCode == "nc") %>%  -->
<!--   dplyr::mutate(Messwert = dplyr::if_else(.data$Einheit == "mg/l", -->
<!--                                           true = .data$Messwert * 1000, -->
<!--                                           false = .data$Messwert), -->
<!--                 Einheit = dplyr::if_else(.data$Einheit == "mg/l", -->
<!--                                           true = "\u00B5g/l", -->
<!--                                           false = .data$Einheit), -->
<!--                 category = as.factor(category)) %>%  -->
<!--   ggplot2::ggplot(mapping = ggplot2::aes(y = forcats::fct_reorder(.data$label,  -->
<!--                                                                   .data$n_above,  -->
<!--                                                                   .desc = TRUE), -->
<!--                                          x = .data$Messwert, -->
<!--                                          fill = .data$category)) + -->
<!--   ggplot2::scale_fill_brewer(palette="RdYlGn") +   -->
<!--   ggplot2::scale_y_discrete(limits = rev) + -->
<!--   ggplot2::scale_x_log10() + -->
<!--   ggplot2::geom_boxplot() + -->
<!--   ggplot2::labs(subtitle = "",                         -->
<!--                 fill = "Category", -->
<!--                 y = "Substance",  -->
<!--                 x = "Concentration (\u00B5g / l)") + -->
<!--   ggplot2::theme_bw() + -->
<!--   ggplot2::theme(legend.position = "top") -->

<!-- g1 -->

<!-- pdff <- "wasserportal_reach-substances_boxplot.pdf" -->
<!-- ggplot2::ggsave(pdff, -->
<!--                 plot = g1,  -->
<!--                 width = 25, -->
<!--                 height = 15,  -->
<!--                 units = "cm") -->

<!-- ``` -->
