---
title: "ThingsBoard Demo (Free Tier)"
author: "Michael Rustler"
date: "`r Sys.time()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ThingsBoard Demo (Free Tier)}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette shows how to push Wasserportal Berlin data into a
[ThingsBoard](https://thingsboard.io) instance — for example the
**free Maker tier** on `https://eu.thingsboard.cloud` (5 devices, 1M data
points/month). The same code works against self-hosted ThingsBoard
Community Edition by changing `TB_HOST`.

## 1. Prerequisites

1. Sign up at <https://eu.thingsboard.cloud> (EU) or
   <https://thingsboard.cloud> (US).
2. Generate an **account API key**:
   *Account > Security > API keys > Generate*. Give it a description like
   `wasserportal-demo` and copy the key once (it is shown only on creation).
3. Install the package and `httr2`:

   ```{r install, eval = FALSE}
   # install.packages("httr2")
   remotes::install_github("kwb-r/wasserportal")
   ```

4. Store credentials as environment variables (e.g. in `~/.Renviron`):

   ```r
   TB_HOST=https://eu.thingsboard.cloud
   TB_API_KEY=<your-api-key>
   ```

   Restart your R session so the variables are loaded.

> **Free-Tier-Limit**: 5 devices. The demo therefore pushes a small
> selection of stations. To push the full Wasserportal dataset you need to
> self-host ThingsBoard CE or upgrade to a paid Cloud tier.

## 2. Pick a Handful of Stations

```{r select}
library(wasserportal)

stations <- wasserportal::get_stations()

# Five well-known Berlin surface water level gauges as a demo selection.
demo_station_ids <- c("5803900", "5805600", "5867000", "5826200", "5824300")
```

## 3. Create Devices in ThingsBoard

`tb_setup_devices()` uses the API key to create one device per
`Messstellennummer` (or returns the id if it already exists) and reads back
the device-specific access token used for telemetry pushes.

```{r setup_devices}
device_tokens <- wasserportal::tb_setup_devices(
  station_ids = demo_station_ids
)

# Names are Messstellennummer, values are tokens. Treat as secret.
str(device_tokens)
```

## 4. Push Station Master Data as Attributes

Static metadata (coordinates, level reference, operator) is sent once per
station as ThingsBoard *attributes*. They show up under the device's
*Attributes > Server* tab and can be referenced from widgets and rule
chains.

```{r push_attributes}
sw_master_urls <- stations$overview_list$surface_water.water_level |>
  dplyr::filter(.data$Messstellennummer %in% demo_station_ids) |>
  dplyr::pull(.data$stammdaten_link)

sw_master <- wasserportal::get_wasserportal_masters_data(
  master_urls = sw_master_urls
)

for (station_id in demo_station_ids) {
  master_row <- sw_master[sw_master$Nummer == station_id, ]
  if (nrow(master_row) == 0L) next

  wasserportal::tb_push_station_attributes(
    attributes = as.list(master_row[1L, ]),
    device_token = device_tokens[[station_id]]
  )
}
```

## 5. Push Daily Time Series

The `get_daily_surfacewater_data()` result is keyed by parameter; for the
demo we push the daily water level (`Tagesmittelwert`).

```{r push_telemetry}
variables <- wasserportal::get_surfacewater_variables()

sw_data_daily <- wasserportal::get_daily_surfacewater_data(
  stations  = stations,
  variables = variables["surface_water.water_level"]
)

water_level <- sw_data_daily$surface_water.water_level

for (station_id in demo_station_ids) {
  one_station <- water_level[water_level$Messstellennummer == station_id, ]
  if (nrow(one_station) == 0L) next

  wasserportal::tb_push_station_telemetry(
    data         = one_station,
    device_token = device_tokens[[station_id]],
    ts_col       = "Datum",
    value_col    = "Tagesmittelwert",
    key_col      = "Parameter"
  )
}
```

To push groundwater data the call is identical apart from the value column:

```{r push_groundwater}
gw_data <- wasserportal::get_groundwater_data(
  stations_list = stations$overview_list[
    grepl("groundwater", names(stations$overview_list))
  ]
)

# Pick five groundwater level stations for the free tier
gwl <- gw_data$groundwater.level
gwl_demo_ids <- unique(as.character(gwl$Messstellennummer))[1:5]
gwl_tokens <- wasserportal::tb_setup_devices(
  station_ids = gwl_demo_ids,
  name_prefix = "wasserportal-gwl-"
)

for (station_id in gwl_demo_ids) {
  one_station <- gwl[gwl$Messstellennummer == station_id, ]
  wasserportal::tb_push_station_telemetry(
    data         = one_station,
    device_token = gwl_tokens[[station_id]],
    value_col    = "Messwert"
  )
}
```

## 6. Visualise in ThingsBoard

After the pushes, open the *wasserportal* dashboard in ThingsBoard:

1. *Add widget > Charts > Time series chart*.
2. Datasource: pick one of the `wasserportal-*` devices.
3. As key, choose the parameter you pushed (e.g. `Wasserstand` for surface
   water level).
4. Adjust the time window in the top-right; Wasserportal data starts in the
   early 2000s for many stations, so set the window wide on first view.

For multiple stations on one chart, add several datasources to the same
widget. Coordinates pushed as attributes can be used to drop pins on the
*Map* widget.

## 7. Re-Running and Idempotency

* `tb_setup_devices()` is idempotent — re-running it returns the existing
  device tokens.
* Telemetry POSTs are **not** deduplicated by ThingsBoard. Re-running the
  push will create duplicate points at the same timestamp. For incremental
  daily updates, filter `Datum > <last successful run>` before calling
  `tb_push_station_telemetry()` (e.g. by storing the last timestamp as a
  server attribute).

## 8. Switching to Self-Hosted CE

When you outgrow the 5-device free-tier limit, the only change required is
the `TB_HOST` environment variable:

```r
Sys.setenv(TB_HOST = "https://thingsboard.your-domain.example")
```

The same R code now talks to your own ThingsBoard CE deployment. Devices,
tokens and pushes all use the same endpoints.
