---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
is_ghactions <- identical(Sys.getenv("CI"), "true")
```

## Stations

### General overview



```{r stations_overview}
# install.packages("remotes")
# remotes::install_github("kwb-r/wasserportal", upgrade = "never", force = TRUE)
library(wasserportal)
overview_options <- wasserportal::get_overview_options()
str(overview_options)

system.time(stations <- wasserportal::get_stations())

str(stations)

jsonlite::write_json(stations$crosstable, 
                     path = "stations_crosstable.json",
                     pretty = TRUE)
```

```{r stations_crosstable}
DT::datatable(stations$crosstable, filter = "top", caption = "Data availabilty 
              per monitoring station")
```

```{r input_ghactions0, echo=FALSE, results='asis', eval=is_ghactions}
cat("The crosstable data for checking data availabilty of the monitoring stations 
is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_crosstable.json](../stations_crosstable.json)
")
```

### GW level

#### Master data 

Overview data of GW level stations can be requested as shown below:

```{r stations_gwl_table_overview}

DT::datatable(stations$overview_list$groundwater.level, filter = "top")

```

Master data of GW level stations can be requested as shown below:

```{r stations_gwl_table_master}
stations_gwl_master <- wasserportal::get_wasserportal_masters_data(
  station_ids = stations$overview_list$groundwater.level$Messstellennummer
)

jsonlite::write_json(stations_gwl_master, 
                     path = "stations_gwl_master.json",
                     pretty = TRUE)

DT::datatable(stations_gwl_master, filter = "top")

``` 

```{r input_ghactions1, echo=FALSE, results='asis', eval=is_ghactions}
cat("The master data of GW level stations is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_gwl_master.json](../stations_gwl_master.json)
")
```

#### Trend Classification 

GW level trend classification (provided by SenWeb) is visualized below.

##### Trend Classification Histogramm

```{r stations_gwl_trend}

gwl <- stations$overview_list$groundwater.level %>% 
  dplyr::mutate(Datum = as.Date(Datum, format = "%d.%m.%Y"))

levels_ordered <- c("extrem niedrig",
                    "sehr niedrig",
                    "niedrig", 
                    "normal",
                    "hoch",
                    "sehr hoch",
                    "extrem hoch",
                    "keine")

text_low_levels <- c("extrem niedrig", "sehr niedrig", "niedrig")
text_high_levels <- c("hoch", "sehr hoch", "extrem hoch")

gwl$Klassifikation <- forcats::fct_relevel(gwl$Klassifikation, levels_ordered)

gwl_classified_only <- gwl %>% dplyr::filter(Klassifikation != "keine")

percental_share_low_levels <- 100*sum(gwl_classified_only$Klassifikation %in% text_low_levels)/nrow(gwl_classified_only) 

percental_share_high_levels <- 100*sum(gwl_classified_only$Klassifikation %in% text_high_levels)/nrow(gwl_classified_only) 

title_text <- sprintf("GW level classification (n = %d out of %d have 'classification' data)", nrow(gwl_classified_only), nrow(gwl))

g1 <- gwl_classified_only %>% 
  dplyr::count(Klassifikation, Grundwasserspannung) %>% 
  dplyr::mutate(percental_share = 100 * n / nrow(gwl)) %>% 
  ggplot2::ggplot(ggplot2::aes_string(x = "Klassifikation",
                                      y = "percental_share",
                                      fill = "Grundwasserspannung")) +
  ggplot2::geom_bar(stat = "identity") + 
  ggplot2::labs(title = title_text,
                x = "Classification",
                y = "Percental share (%)") +
  ggplot2::theme_bw()

plotly::ggplotly(g1)

```

`r round(percental_share_low_levels,2)` percent of all considered `r nrow(gwl_classified_only)` 
GW level monitoring stations containing `classification` data (out of `r nrow(gwl)`
provided by SenWeb) indicate `below normal` (`r paste(text_low_levels, collapse=", ")`)
GW levels. However, only `r round(percental_share_low_levels,2)` percent are 
indicate `above normal` (`r paste(text_high_levels, collapse=", ")`) GW levels.

##### Trend Classification Map

```{r stations_gwl_trend_spatially}
level_colors <- data.frame(Klassifikation = levels_ordered, 
                           classi_color = c("darkred", 
                                            "red", 
                                            "orange", 
                                            "green",
                                            "lightblue", 
                                            "blue", 
                                            "darkblue",
                                            "grey"))

gwl_classified_only_with_coords <- gwl_classified_only %>% 
  dplyr::mutate(Messstellennummer = as.character(Messstellennummer),
                label_text = paste("Messstellennummer:", 
                                    Messstellennummer, 
                                    "; ",
                                    "Grundwasserspannung:", 
                                    Grundwasserspannung, 
                                    ";",
                                    "Klassifikation:", 
                                    Klassifikation,
                                   ";",
                                   "Datum:",
                                   Datum
                                   )) %>% 
  dplyr::left_join(stations_gwl_master %>%
                     dplyr::select("Nummer", 
                                   "Rechtswert_UTM_33_N",
                                   "Hochwert_UTM_33_N") %>% 
                     dplyr::rename(Messstellennummer = "Nummer"),
                   by = "Messstellennummer") %>% 
  dplyr::left_join(level_colors, by = "Klassifikation") %>% 
  sf::st_as_sf(coords = c("Rechtswert_UTM_33_N", "Hochwert_UTM_33_N"),
               crs = 25833) %>% 
  sf::st_transform(crs = 4326)



  gwlmap <- gwl_classified_only_with_coords %>% 
  leaflet::leaflet() %>%
  leaflet::addTiles() %>% 
  leaflet::addProviderTiles(leaflet::providers$CartoDB.Positron) %>% 
  leaflet::addCircles(color = ~classi_color,
                      label = ~label_text) %>% 
  leaflet::addLegend(position = "topright",
                     colors = level_colors$classi_color,
                     labels = level_colors$Klassifikation,
                     title = sprintf("Classification (latest data: %s)",
                                     max(gwl_classified_only_with_coords$Datum))
                     )
  
  htmlwidgets::saveWidget(gwlmap, 
                          "./map_gwl-trend.html", 
                          title = "GW level trend")
  
  gwlmap
```

```{r input_ghactions_map, echo=FALSE, results='asis', eval=is_ghactions}
cat("GW level trend plot is also available on a full html page here:
[https://kwb-r.github.io/wasserportal/map_gwl-trend.html](../map_gwl-trend.html)
")
```

#### Download and Plotting 

for total period available.

```{r test_gwl_download}
station_gwl <- stations$overview_list$groundwater.level[1,]
ncols <- 2:ncol(station_gwl)

gw_level <- wasserportal::read_wasserportal_raw_gw(
  station = station_gwl$Messstellennummer, 
  stype = "gwl")
names(gw_level) <-  kwb.utils::substSpecialChars(names(gw_level))
head(gw_level)

g <- ggplot2::ggplot(gw_level, ggplot2::aes_string(x = "Datum", y = "GW_Stand_m_ue_NHN")) +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()


title_subtitle <- paste0(paste0(names(station_gwl)[1], ": ", 
                             station_gwl[1], 
                             collapse =", "),
       "<br>",
       "<sup>",
       paste0(names(station_gwl)[ncols], ": ",
              station_gwl[ncols], 
              collapse =", "),
       "</sup>")


plotly::ggplotly(g) %>%
  plotly::layout(title = list(text = title_subtitle))
```

### GW quality

Overview data of GW level stations can be requested as shown below:


```{r stations_gwq_table_overview}
stations_gwq <- wasserportal::get_wasserportal_stations_table(
  type = overview_options$groundwater$quality
  )

DT::datatable(stations_gwq, filter = "top")
```

Master data of GW quality stations can be requested as shown below:

```{r stations_gwq_table_master}
stations_gwq_master <- wasserportal::get_wasserportal_masters_data(
  station_ids = stations_gwq$Messstellennummer
)

jsonlite::write_json(stations_gwq_master, 
                     path = "stations_gwq_master.json",
                     pretty = TRUE)

``` 

```{r input_ghactions2, echo=FALSE, results='asis', eval=is_ghactions}
cat("The master data of GW quality stations is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_gwq_master.json](../stations_gwq_master.json)
")
```

#### Download and Plotting One Station

```{r test_gwq_download_single}
station_gwq <- stations$overview_list$groundwater.quality[1,]
ncols <- 2:ncol(station_gwq)

gw_quality <- wasserportal::read_wasserportal_raw_gw(
  station = station_gwq$Messstellennummer, 
  stype = "gwq")
head(gw_quality)

unique(gw_quality$Parameter)

g <- gw_quality %>%  
dplyr::filter(Parameter == "Sulfat") %>% 
ggplot2::ggplot(ggplot2::aes_string(x = "Datum", y = "Messwert", col = "Parameter")) +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()


title_subtitle <- paste0(paste0(names(station_gwq)[1], ": ", 
                             station_gwq[1], 
                             collapse =", "),
       "<br>",
       "<sup>",
       paste0(names(station_gwq)[ncols], ": ",
              station_gwq[ncols], 
              collapse =", "),
       "</sup>")


plotly::ggplotly(g) %>%
  plotly::layout(title = list(text = title_subtitle))
```

#### Download and Plotting Multiple Stations

```{r test_gwq_download_multiple}
station_gwq <- stations$overview_list$groundwater.quality[1,]
ncols <- 2:ncol(station_gwq)

# Plot 10 GW quality 
selected_stations <- stations$overview_list$groundwater.quality$Messstellennummer[1:10]

gw_quality_multi <- data.table::rbindlist(
  lapply(selected_stations, 
                     function(id) {
                       wasserportal::read_wasserportal_raw_gw(
                         station = id, stype = "gwq")
                     }))


jsonlite::write_json(gw_quality_multi,
                     path = "stations_gwq_data.json",
                     pretty = TRUE)

g <- gw_quality_multi %>%  
dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
dplyr::filter(Parameter == "Sulfat") %>% 
ggplot2::ggplot(ggplot2::aes_string(x = "Datum", 
                                    y = "Messwert", 
                                    col = "Messstellennummer")) +
ggplot2::labs(title = "GW quality (Sulfat)") +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()

plotly::ggplotly(g)
```

```{r input_ghactions2, echo=FALSE, results='asis', eval=is_ghactions}
cat("The data of all GW quality stations is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_gwq_data.json](../stations_gwq_data.json)
")
