---
title: "Tutorial"
author: "Michael Rustler"
date: "`r Sys.time()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
is_ghactions <- identical(Sys.getenv("CI"), "true")
```

## Stations

### General overview



```{r stations_overview}
# install.packages("remotes")
# remotes::install_github("kwb-r/wasserportal", upgrade = "never", force = TRUE)
library(wasserportal)
overview_options <- wasserportal::get_overview_options()
str(overview_options)

system.time(stations <- wasserportal::get_stations())

str(stations)

jsonlite::write_json(stations$crosstable, 
                     path = "stations_crosstable.json",
                     pretty = TRUE)
```

```{r stations_crosstable}
DT::datatable(stations$crosstable, filter = "top", caption = "Data availabilty 
              per monitoring station")
```

```{r input_ghactions0, echo=FALSE, results='asis', eval=is_ghactions}
cat("The crosstable data for checking data availabilty of the monitoring stations 
is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_crosstable.json](../stations_crosstable.json)
")
```

### GW level

#### Master data 

Overview data of GW level stations can be requested as shown below:

```{r stations_gwl_table_overview}

DT::datatable(stations$overview_list$groundwater.level, filter = "top")

```

Master data of GW level stations can be requested as shown below:

```{r stations_gwl_table_master}
stations_gwl_master <- wasserportal::get_wasserportal_masters_data(
  master_urls = stations$overview_list$groundwater.level$stammdaten_link
)

jsonlite::write_json(stations_gwl_master, 
                     path = "stations_gwl_master.json",
                     pretty = TRUE)

DT::datatable(stations_gwl_master, filter = "top")

``` 

```{r input_ghactions1, echo=FALSE, results='asis', eval=is_ghactions}
cat("The master data of GW level stations is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_gwl_master.json](../stations_gwl_master.json)
")
```

#### Trend Classification 

GW level trend classification (provided by SenWeb) is visualized below.

##### Trend Classification Histogramm

```{r stations_gwl_trend}

gwl <- stations$overview_list$groundwater.level %>% 
  dplyr::mutate(Datum = as.Date(Datum, format = "%d.%m.%Y"))

text_low_levels <- c("extrem niedrig", "sehr niedrig", "niedrig")
text_high_levels <- c("hoch", "sehr hoch", "extrem hoch")
levels_ordered <- c(text_low_levels, "normal", text_high_levels, "keine")

gwl$Klassifikation <- forcats::fct_relevel(gwl$Klassifikation, levels_ordered)

gwl_classified_only <- gwl %>% dplyr::filter(Klassifikation != "keine")

percental_share_low_levels <- 100*sum(gwl_classified_only$Klassifikation %in% text_low_levels)/nrow(gwl_classified_only) 

percental_share_high_levels <- 100*sum(gwl_classified_only$Klassifikation %in% text_high_levels)/nrow(gwl_classified_only) 

title_text <- sprintf("GW level classification (n = %d out of %d have 'classification' data)", nrow(gwl_classified_only), nrow(gwl))

g1 <- gwl_classified_only %>% 
  dplyr::count(Klassifikation, Grundwasserspannung) %>% 
  dplyr::mutate(percental_share = 100 * n / nrow(gwl)) %>% 
  ggplot2::ggplot(ggplot2::aes_string(x = "Klassifikation",
                                      y = "percental_share",
                                      fill = "Grundwasserspannung")) +
  ggplot2::geom_bar(stat = "identity") + 
  ggplot2::labs(title = title_text,
                x = "Classification",
                y = "Percental share (%)") +
  ggplot2::theme_bw()

plotly::ggplotly(g1)

```

`r round(percental_share_low_levels,2)` percent of all considered `r nrow(gwl_classified_only)` 
GW level monitoring stations containing `classification` data (out of `r nrow(gwl)`
provided by SenWeb) indicate `below normal` (`r paste(text_low_levels, collapse=", ")`)
GW levels. However, only `r round(percental_share_low_levels,2)` percent are 
indicate `above normal` (`r paste(text_high_levels, collapse=", ")`) GW levels.

##### Trend Classification Map

```{r stations_gwl_trend_spatially}
level_colors <- data.frame(Klassifikation = levels_ordered, classi_color = c(
  "darkred", "red", "orange", "green", "lightblue", "blue", "darkblue", "grey"
))

gwl_classified_only_with_coords <- gwl_classified_only %>% 
  dplyr::mutate(
    Messstellennummer = as.character(Messstellennummer),
  ) %>% 
  dplyr::left_join(
    stations_gwl_master %>%
      dplyr::select("Nummer", "Rechtswert_UTM_33_N", "Hochwert_UTM_33_N") %>% 
      dplyr::rename(Messstellennummer = "Nummer"),
    by = "Messstellennummer"
  ) %>% 
  dplyr::left_join(
    level_colors, 
    by = "Klassifikation"
  ) %>% 
  sf::st_as_sf(
    coords = c("Rechtswert_UTM_33_N", "Hochwert_UTM_33_N"),
    crs = 25833
  ) %>% 
  sf::st_transform(crs = 4326)

# Create a vector of labels for each row in gwl_classified_only_with_coords
labs <- wasserportal::columns_to_labels(
  data = gwl_classified_only_with_coords, 
  columns = c(
    "Messstellennummer", 
    "Grundwasserspannung", 
    "Klassifikation", 
    "Datum"
  ),
  fmt = "<p>%s: %s</p>",
  sep = ""
)

# Print Map
gwlmap <- gwl_classified_only_with_coords %>% 
  leaflet::leaflet() %>%
  leaflet::addTiles() %>% 
  leaflet::addProviderTiles(leaflet::providers$CartoDB.Positron) %>%
  leaflet::addCircles(
    color = ~classi_color,
    label = lapply(labs, htmltools::HTML)
  ) %>% 
  leaflet::addLegend(
    position = "topright",
    colors = level_colors$classi_color,
    labels = level_colors$Klassifikation,
    title = sprintf(
      "Classification (latest data: %s)",
      max(gwl_classified_only_with_coords$Datum)
    )
  )

htmlwidgets::saveWidget(
  gwlmap, 
  "./map_gwl-trend.html", 
  title = "GW level trend"
)

gwlmap
```

```{r input_ghactions_map, echo=FALSE, results='asis', eval=is_ghactions}
cat("GW level trend plot is also available on a full html page here:
[https://kwb-r.github.io/wasserportal/map_gwl-trend.html](../map_gwl-trend.html)
")
```

#### Download and Plotting One Station

for total period available.

```{r test_gwl_download_single, eval = FALSE}
station_gwl <- stations$overview_list$groundwater.level[1,]
ncols <- 2:ncol(station_gwl)

gw_level <- wasserportal::read_wasserportal_raw_gw(
  station = station_gwl$Messstellennummer, 
  stype = "gwl") %>% 
dplyr::mutate(Label = sprintf("%s (%s)", Parameter, Einheit))
head(gw_level)

g <- gw_level %>% 
ggplot2::ggplot(ggplot2::aes_string(x = "Datum", y = "Messwert", col = "Label")) +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()


title_subtitle <- paste0(paste0(names(station_gwl)[1], ": ", 
                             station_gwl[1], 
                             collapse =", "),
       "<br>",
       "<sup>",
       paste0(names(station_gwl)[ncols], ": ",
              station_gwl[ncols], 
              collapse =", "),
       "</sup>")


plotly::ggplotly(g) %>%
  plotly::layout(title = list(text = title_subtitle))
```

#### Download and Plotting Multiple Stations

```{r test_gwl_download_multiple, eval = FALSE}
debug <- FALSE
gw_level_multi <- data.table::rbindlist(
  lapply(stations$overview_list$groundwater.level$Messstellennummer, 
                     function(id) {
                       kwb.utils::catAndRun(sprintf("Downloading Messstellennummer == '%s'",
                                                    id), 
                                            expr = {
                       wasserportal::read_wasserportal_raw_gw(
                         station = id, stype = "gwl")
                     }, 
                     dbg = debug)}))


readr::write_csv(gw_level_multi, 
                 file = "groundwater_level.csv")


# Plot 10 GW level
selected_stations <- stations$overview_list$groundwater.level$Messstellennummer[1:10]

g <- gw_level_multi %>% 
dplyr::filter(Messstellennummer %in% selected_stations) %>% 
dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
ggplot2::ggplot(ggplot2::aes_string(x = "Datum", 
                                    y = "Messwert", 
                                    col = "Messstellennummer")) +
ggplot2::labs(title = "GW level (m above NN)") +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()

plotly::ggplotly(g)
```

```{r input_ghactions_gwl_download, echo=FALSE, results='asis', eval=is_ghactions}
cat("The data of all GW level stations is also available in CSV format here:
[https://kwb-r.github.io/wasserportal/groundwater_level.csv](../groundwater_level.csv)
")
```


### GW quality

Overview data of GW level stations can be requested as shown below:


```{r stations_gwq_table_overview}
stations_gwq <- wasserportal::get_wasserportal_stations_table(
  type = overview_options$groundwater$quality
  )

DT::datatable(stations_gwq, filter = "top")
```

Master data of GW quality stations can be requested as shown below:

```{r stations_gwq_table_master}
stations_gwq_master <- wasserportal::get_wasserportal_masters_data(
  master_urls = stations_gwq$stammdaten_link
)

jsonlite::write_json(stations_gwq_master, 
                     path = "stations_gwq_master.json",
                     pretty = TRUE)

``` 

```{r input_ghactions2, echo=FALSE, results='asis', eval=is_ghactions}
cat("The master data of GW quality stations is also available in JSON format here:
[https://kwb-r.github.io/wasserportal/stations_gwq_master.json](../stations_gwq_master.json)
")
```

#### GW Quality: Download and Plotting One Station

```{r test_gwq_download_single, eval = FALSE}
station_gwq <- stations$overview_list$groundwater.quality[1,]
ncols <- 2:ncol(station_gwq)

gw_quality <- wasserportal::read_wasserportal_raw_gw(
  station = station_gwq$Messstellennummer, 
  stype = "gwq")
head(gw_quality)

unique(gw_quality$Parameter)

g <- gw_quality %>%  
dplyr::filter(Parameter == "Sulfat") %>% 
ggplot2::ggplot(ggplot2::aes_string(x = "Datum", y = "Messwert", col = "Parameter")) +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()


title_subtitle <- paste0(paste0(names(station_gwq)[1], ": ", 
                             station_gwq[1], 
                             collapse =", "),
       "<br>",
       "<sup>",
       paste0(names(station_gwq)[ncols], ": ",
              station_gwq[ncols], 
              collapse =", "),
       "</sup>")


plotly::ggplotly(g) %>%
  plotly::layout(title = list(text = title_subtitle))
```

#### GW Quality: Download and Plotting Multiple Stations

```{r test_gwq_download_multiple, eval = FALSE}
debug <- FALSE
gw_quality_multi <- data.table::rbindlist(
  lapply(stations$overview_list$groundwater.quality$Messstellennummer, 
                     function(id) {
                       kwb.utils::catAndRun(sprintf("Downloading Messstellennummer == '%s'",
                                                    id), 
                                            expr = {
                       wasserportal::read_wasserportal_raw_gw(
                         station = id, stype = "gwq")
                     }, 
                     dbg = debug)}))


readr::write_csv(gw_quality_multi,
                 "groundwater_quality.csv")


# Plot 10 GW quality 
selected_stations <- stations$overview_list$groundwater.quality$Messstellennummer[1:10]

g <- gw_quality_multi %>% 
dplyr::filter(Messstellennummer %in% selected_stations) %>% 
dplyr::mutate(Messstellennummer = as.character(Messstellennummer)) %>% 
dplyr::filter(Parameter == "Sulfat") %>% 
ggplot2::ggplot(ggplot2::aes_string(x = "Datum", 
                                    y = "Messwert", 
                                    col = "Messstellennummer")) +
ggplot2::labs(title = "GW quality (Sulfat)") +
ggplot2::geom_line() +
ggplot2::geom_point() +
ggplot2::theme_bw()

plotly::ggplotly(g)
```

```{r input_ghactions_gwq_download, echo=FALSE, results='asis', eval=is_ghactions}
cat("The data of all GW quality stations is also available in CSV format here:
[https://kwb-r.github.io/wasserportal/groundwater_quality.csv](../groundwater_quality.csv)
")
